
#**Plots**

First, load the required libraries

```{r}
library(ggplot2)
library(gapminder)
library(dplyr)
```


####**1) Plot 1**
```{r}
ggplot(data = gapminder, aes(x = gdpPercap, 
                             y = lifeExp, 
                             by = continent)) +  # begin by specifying dataset, axis, and grouping
  geom_point(aes(color = continent, 
                 shape = continent))   # Now, create a scatter plot by creating a layer. Specify how the variables are displayed on the graph.
 # individually changes the shape for each continent
```
  
####**2) Plot 2**
```{r}
ggplot(data = gapminder, aes(x = gdpPercap, 
                             y = lifeExp, 
                             by = continent)) + 
  geom_point(aes(color = continent, 
                 shape = continent)) +
  scale_x_log10()  # Transform the scale of a specified axis with this command. Other transformations can be used instead of log10.
```  
  
####**3) Plot 3**
```{r}
ggplot(data = gapminder, aes(x = gdpPercap, 
                             y = lifeExp, 
                             by = continent)) + 
  geom_point(aes(color = continent, 
                 shape = continent)) +
  scale_x_log10() +
  geom_smooth(method = lm, aes(group = 1))  # by putting a group in, it's really just specifying not to group by continent. can also just remove by = continent from above.
``` 
  
####**4) Plot 4** 
```{r}
ggplot(data = gapminder, aes(x = lifeExp, 
                             fill = continent)) +
      geom_density(kernel = 'gaussian', 
                   aes(),
                   alpha = .4, 
                   size = .75) +
      facet_wrap(~ year)  # tells it which variable to facet the plots by. Fun to play with, I made a huge plot faceting by country and a useless one faceting by continent.
```

####**5) Plot 5**
```{r}
ggplot(data = gapminder, 
       aes(x = continent, 
           y = lifeExp)) +
      geom_boxplot(aes(color = continent)) +
      theme(axis.text.x = element_text(angle = -90)) +  # an example of a layer that adjusts the axis text in more elaborate ways than just size. Still just scratching the surface here, but at least this makes it readable.
      facet_wrap(~ year)
```      
####**6) Plot 6**
```{r}
ggplot(data = gapminder, aes(x = lifeExp, 
                             fill = continent)) +
      geom_density(kernel = 'gaussian', 
                   aes(), 
                   alpha = .4)
                
```
Nothing to see here, this one was easy.

####**7) Plot 7**
```{r}
str(gapminder)  # Check the structure of gapminder before messing around too much with dplyr, just to get your head on straight
```

```{r}
filter(gapminder, continent == 'Asia') %>%  # I only want data about Asia so it's safe to filter out everything else
ggplot(aes(x = lifeExp, 
           fill = continent)) +
      geom_density(kernel = 'gaussian', 
                   aes(), 
                   alpha = .4) +
      scale_fill_manual(values = c('green')) +
      geom_vline(aes(xintercept = mean(lifeExp))) # this was a serious pain, I had trouble finding a concise write up on geom_vline. After an hour struggle, I realized I had mispelled xintercept, woops.
```
      
    
####**8) Plot 8**

First I made a new data frame with only continent and mean life expectancy

```{r}
mean_life <- data.frame(group_by(gapminder, continent) %>%  
    summarise(mean = mean(lifeExp)))
```
Then I plotted it.

```{r}
ggplot(data = gapminder, 
       aes(x = lifeExp, 
           fill = continent)) +              
      geom_density(kernel = 'gaussian', 
                   aes(), 
                   alpha = .4) +
      geom_vline(data = mean_life, 
                 aes(xintercept = mean)) +  # be sure to point it to the new data table here. I almost confused myself by having the column named mean, is there a standard protocol about not naming things the same as a function?
      facet_wrap(~ continent) 
```      
      
      
      
#**Find the mistakes**

load the modified gapinder dataset

```{r}
library(ggplot2)

hw_gapminder <- read.csv('C:/Users/Rosen_000/Downloads/hw_gapminder.csv')

str(hw_gapminder)
```

####**1) Given:**

```{r, eval = FALSE}
mean_lifeExp <- mean(hw_gapminder$lifeExpe)
```

####**Fixed:**
    
```{r}
mean_lifeExp<- mean(hw_gapminder$lifeExp)  # spelling: removed the extra "e" at the end 
mean_lifeExp
```

####**2) Given:**

```{r, eval = FALSE}
small_set <- hw_gapminder[c(1, 2, 3, 4, 1300:1304), ('country', 'continent', 'year')]
```

####**Fixed:**
```{r}
small_set <- hw_gapminder[c(1, 2, 3, 4, 1300:1304), c('country', 'continent', 'year')]  # syntax: added a "c" before the list of columns to include
small_set
```

####**3) Given:** 
```{r, eval = FALSE}
mean_gdp <- mean(hw_gapminder$gdpPercap)
```
####**Fixed:**
```{r}    
mean_gdp <- mean(hw_gapminder$gdpPercap, na.rm = TRUE)  # added na.rm = TRUE, allowing to calculate the mean even though there was some missing data or something in there.
mean_gdp
```
####**Given:**
```{r, eval = FALSE}
max_country <- hw_gapminder$country[which(hw_gapminder$lifeExp = max(hw_gapminder$lifeExp))]
```

####**Fixed:**
```{r}
max_country <- hw_gapminder$country[which(hw_gapminder$lifeExp == max(hw_gapminder$lifeExp))] # syntax: Needed an extra "=", although it generated a sligthly different result than the one on the website; mine showed levels. 
max_country
```
I also achieved a similar result (same answer, looks a little different) using dplyr and slice, which was more intuitive to me.
```{r}
gapminder %>%
    slice(which.max(lifeExp)) %>%
    summarise(country)
```{r}

 